Enforced Invariant Confluence

### 2020-08-07 doc/the_vldb_journal_paper/rebuttal.tex

\paragraph{Reviewer 1: D7}
\begin{feedback}
  In the intro we read about "the trade-off between application complexity and
  coordination-freedom", it would be great to see some practical examples later
  in the paper
\end{feedback}
\textcolor{red}{TODO.}

\paragraph{Reviewer 1: D8}
\begin{feedback}
  In section 4.2, more details about what can be done with respect to help a
  user reason about unreachable states would be great
\end{feedback}
\textcolor{red}{TODO.}

\paragraph{Reviewer 1: D9}
\begin{feedback}
  Figure 5 should be moved before figure 6
\end{feedback}
\textcolor{red}{TODO.}

\paragraph{Reviewer 1: D10}
\begin{feedback}
  in page 3 we read ``The culprit is concurrent decrements, which we can forbid
  in a simple one-segment segmentation ...'', this sentence does not parse well
\end{feedback}
We reworded the sentence to be easier to read.

\paragraph{Reviewer 1: D11}
\begin{feedback}
  In 6.4 we read ``This example is exactly the same as Example 8 which we
  handled by simply removing withdrawal transactions from our segmentation's
  set of transactions.'' How can one identify transactions to remove, and is
  the removal practically done?
\end{feedback}
Users must manually identify transactions to remove. More generally,
identifying a transaction to remove from a segmentation is a special case of
forming a segmentation, and we do not provide any automated assistance on how
to form a segmentation. Is the removal practically done? That depends on the
workload. For some workloads, identifying invariant-violating transactions can
be easy. The bank withdrawal example (Example 8). Other, more complex
workloads, can be difficult to reason about. Forming segmentations for these
workloads is not easy. We think that automatically forming segmentations is an
interesting avenue for future research.

\paragraph{Reviewer 1: D12}
\begin{feedback}
  In 8.1 we read ``When a server receives a coordination request from the
  leader, it stops processing transactions and sends the leader its state.''
  what happens to the in-flight transactions? Are the cancelled or allowed to
  finish? Is the system simply not admitting new transactions?
\end{feedback}
In-flight transactions are deferred until after the round of coordination is
done. They aren't cancelled, and they are allowed to finish, but only after the
coordination is done. The entire system stops processing transactions
temporarily.  Technically, the system can still \emph{admit} new transactions
during coordination, but it cannot execute them.

We describe this in Section 6.2, for example, when we say that if ``$t \notin
T_i$, then $p_i$ initiates a round of global coordination to execute $t$.
During global coordination, every server temporarily stops processing
transactions.''

Your question also reinforces the conclusion of Figure 10. If coordination is
frequent, then segmented \invariantconfluence{} becomes slow, even slower than
linearizable replication. Segmented \invariantconfluent{} works well only when
coordination is infrequent.
